---
title: "Swiss End-User Electricity Consumption"
output: 
  html_document:
    theme: readable
    toc: FALSE
    toc_depth: 3
    toc_float: TRUE
    df_print: paged
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(broom)
library(readxl)
library(lubridate)

setwd(dirname(rstudioapi::getActiveDocumentContext()[[2]]))
```

***
### Description of the Data
***

The data comes from [Swissgrid](https://www.swissgrid.ch/en/home.html), who regularly update their [total end-user energy consumption data sets](https://www.swissgrid.ch/en/home/operation/grid-data/generation.html) for the Switzerland.

To show only the results, large code chunks are hidden, but can be unfolded by clicking the "Code" boxes on the top right of each hidden code chunk.

***
### Data Cleaning
***

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load data
electricity <- read_xlsx("5 EnergieEndverbrauch2009-2023.xlsx")
```

The annual files were only merged to one. No additional data preparation is needed.

***
### How Did The Pandemic Affect Swiss End-User Energy Consumption?
***

```{r, fig.width=8, fig.height=4.95, dpi=300, dev="png", message=FALSE, warning=FALSE}
# Aggregate to monthly values
elec <- electricity %>%
  mutate(date = as.character(substr(Zeitpunkt,1,10)),
         year = as.character(substr(Zeitpunkt,1,4)),
         month_in_year = month(Zeitpunkt)) %>%
  group_by(year, month_in_year) %>%
  summarise(kWh = sum(kWh),
            month_in_year = last(month_in_year),
            year = last(year)) %>%
  head(-1)

elec %>%
  mutate(kWh = kWh/1000000) %>% 
  ggplot(aes(x = month_in_year, y = kWh, color = as.factor(year))) +
  geom_line(size = 0.7) +
  labs(title = "The effect of the COVID-19 pandemic on total energy consumption in Switzerland",
       subtitle = "End user electricity consumption in the Swiss controlblock by month (in millions of kWh)",
       x = "Calendar Month Number",
       y = "kWh (in millions)") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, face="bold", colour="black"),
        plot.subtitle = element_text(face = "italic", colour = "gray50",
                                   size = 10),
        legend.title = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title = element_text(size = 10)) +
  scale_colour_manual(values = c(rep("gray75", 11), "red", "firebrick", "orange")) +
  scale_x_continuous(breaks = seq(1,12,1), limits = c(1,12)) +
  scale_y_continuous(labels = scales::comma_format())

```

Aggregating the data to monthly values and overlaying them for comparison reveals that the pandemic greatly impacted total energy consumption, especially during the first lockdown.

***
### Are There Daily Patterns Within Each Week?
***

```{r, fig.width=8, fig.height=4.95, dpi=300, dev="png", message=FALSE, warning=FALSE}
elec <- electricity %>% 
  mutate(hour = hour(Zeitpunkt),
         weekday = wday(Zeitpunkt, label = TRUE)) %>% 
  group_by(hour, weekday) %>% 
  summarise(mean_c = mean(kWh)) %>% 
  mutate(weekday = ordered(weekday, levels = c("Mon", "Tue", "Wed", "Thu",
                                               "Fri", "Sat", "Sun")))
elec %>% 
  ggplot(aes(x = hour+1, y = weekday)) +
  geom_tile(aes(fill = mean_c), width=0.95, height=0.95) +
  labs(title = "Swiss End-User Electricity Consumption",
       subtitle = "Averages are formed on 2009-2023",
       y = "Weekday",
       x = "Hour In The Day (Starting At Midnight)",
       fill = "Mean Consumption:") +
  scale_x_continuous(breaks = 1:24,  expand = c(0, 0)) +
  scale_fill_distiller(type = "seq", direction = 1,
                       labels = scales::comma_format(suffix = " kWh")) +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        plot.title = element_text(size = 12, face="bold", colour="black"),
        plot.subtitle = element_text(face = "italic", colour = "gray50",
                                     size = 10),
        axis.title = element_text(size = 10))
```

From the heat map above, it can be seen that peaks take place during weekday business hours, whereas the weekend looks milder. It can be concluded that the industry has a very high impact on total energy consumption.

***
#### Are Holiday Lows Visible?
***

```{r, fig.width=8, fig.height=4.95, dpi=300, dev="png", message=FALSE, warning=FALSE}
electricity %>% 
  mutate(day = yday(Zeitpunkt),
         year = year(Zeitpunkt)) %>% 
  group_by(day) %>% 
  summarise(mean_kWh = mean(kWh),
            lower_kWh = quantile (kWh, 0.1),
            higher_kWh = quantile(kWh, 0.9)) %>% 
  ggplot(aes(day, mean_kWh)) +
  geom_line(colour = "dodgerblue", size = 0.75) +
  geom_ribbon(aes(ymin = lower_kWh, ymax = higher_kWh),
              colour = "dodgerblue", fill = "dodgerblue",
              alpha = 0.5) +
  labs(title = "Daily Averages With Confidence Levels (10th And 90th Percentile)",
       subtitle = "Averages are formed based on historical data from the period 2009-2022",
       y = "kWh",
       x = "Day In The Year") +
  scale_y_continuous(labels = scales::comma_format()) +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, face="bold", colour="black"),
        plot.subtitle = element_text(face = "italic", colour = "gray50",
                                     size = 10),
        axis.title = element_text(size = 10))
```

### Total Usage by Weekday vs. Weekend

```{r}
electricity %>% 
  group_by(date = date(Zeitpunkt)) %>% 
  summarise(usage = sum(kWh, na.rm = T) / 1e6) %>% 
  ungroup() %>% 
  mutate(wday = wday(date, week_start = 1),
         indicator = case_when(
           wday <= 5 ~ "Workday",
           wday == 6 ~ "Saturday",
           wday == 7 ~ "Sunday",
         ) %>% 
           factor(levels = c("Workday", "Saturday", "Sunday")),
         yday = yday(date)) %>% 
  ggplot(aes(yday, usage, colour = indicator)) +
  geom_point(alpha = 0.33, size = 1.5) +
  labs(y = "Swiss Electricity Consumption",
       colour = NULL, x = "Day of Year") +
  scale_colour_manual(values =  c("dodgerblue",
                                  "darkorchid2",
                                  "azure3")) +
  scale_y_continuous(limits = c(100, 210),
                     labels = scales::comma_format(suffix = " GWh")) +
  theme(panel.background = element_rect(fill = "black", colour = "black"),
        plot.background = element_rect(fill = "black", colour = "black"),
        legend.background = element_rect(fill = "black"),
        legend.key = element_rect(fill = "black"),
        legend.text = element_text(colour = "grey50", size = 16),
        plot.title = element_text(face = "bold", colour = "grey50",
                                  hjust = 0.5, size = 16),
        panel.grid.major = element_line(colour = "grey10"),
        panel.grid.minor = element_line(colour = "grey10"),
        legend.position = "right",
        legend.margin = margin(0, 0, 0, 0),
        plot.margin = margin(5, 0, 5, 0),
        panel.border = element_blank(),
        # axis.text.x = element_blank(),
        axis.text = element_text(colour = "grey50", size = 14),
        axis.title = element_text(colour = "grey50", size = 14))

ratio = 25.5/6.4
height = 3.5
width = height * ratio
ggsave(filename = "LinkedIn Banner.png", dpi = 300,
       width = width, height = height)


```

```{r, fig.width=8, fig.height=4.95, dpi=300, dev="png", message=FALSE, warning=FALSE}
electricity %>% 
  mutate(Zeitpunkt = round_date(Zeitpunkt, unit = "hour")) %>% 
  group_by(Zeitpunkt) %>% 
  summarise(kWh = sum(kWh, na.rm = T)) %>% 
  ungroup() %>%
  mutate(hour = hour(Zeitpunkt),
         week = week(Zeitpunkt)) %>% 
  group_by(hour, week) %>% 
  summarise(mean_c = median(kWh, na.rm = T)/1e6) %>% 
  ungroup() %>%
  ggplot(aes(y = hour + 1, x = week)) +
  geom_tile(aes(fill = mean_c), width=1, height=1, alpha = 0.9) +
  labs(title = "Median Swiss Electricity Consumption by Hour in Day and Week in Year",
       y = NULL,
       x = NULL,
       fill = NULL) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(2, 52, 2)) +
  scale_y_reverse(expand = c(0, 0)) +
  guides(fill = guide_colourbar(barwidth = 20, barheight = 0.25)) +
  scale_fill_gradient(low = "black", high = "dodgerblue",
                      labels = scales::comma_format(suffix = " GWh")) +
  theme(panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        legend.background = element_rect(fill = "black"),
        legend.key = element_rect(fill = "black"),
        legend.position = "bottom",
        legend.text = element_text(colour = "grey50", size = 12),
        legend.title = element_text(colour = "grey50"),
        legend.margin = margin(0, 0, 0, 0),
        plot.title = element_text(face = "bold", colour = "grey50",
                                  hjust = 0.5, size = 14),
        plot.subtitle = element_text(colour = "grey50", hjust = 0.5),
        panel.grid.major = element_line(colour = "grey10"),
        panel.grid.minor = element_line(colour = "grey10"),
        plot.margin = margin(10, 10, 10, 10),
        panel.border = element_blank(),
        axis.text = element_text(colour = "grey50", size = 14),
        axis.title = element_text(colour = "grey50", size = 14))

ratio = 25.5/6.4
height = 3.5
width = height * ratio
ggsave(filename = "LinkedIn Banner2.png", dpi = 300,
       width = width, height = height)
```

# No text at all, keep just the plot itself

### Total Usage by Weekday vs. Weekend

```{r}
electricity %>% 
  group_by(date = date(Zeitpunkt)) %>% 
  summarise(usage = sum(kWh, na.rm = T) / 1e6) %>% 
  ungroup() %>% 
  mutate(wday = wday(date, week_start = 1),
         indicator = case_when(
           wday <= 5 ~ "Workday",
           wday == 6 ~ "Saturday",
           wday == 7 ~ "Sunday",
         ) %>% 
           factor(levels = c("Workday", "Saturday", "Sunday")),
         yday = yday(date)) %>% 
  ggplot(aes(yday, usage, colour = indicator)) +
  geom_point(alpha = 0.33, size = 1.5) +
  labs(y = NULL, x = NULL,
       colour = NULL, x = "Day of Year") +
  scale_colour_manual(values =  c("dodgerblue",
                                  "darkorchid2",
                                  "azure3")) +
  scale_y_continuous(labels = scales::comma_format(suffix = " GWh")) + 
  geom_line(stat="smooth", linewidth = 1, alpha = 0.5) +
  coord_cartesian(xlim = c(17, 351), ylim = c(104, 218)) +
  guides(colour = "none") +
  theme(panel.background = element_rect(fill = "black", colour = "black"),
        plot.background = element_rect(fill = "black", colour = "black"),
        legend.background = element_rect(fill = "black"),
        legend.key = element_rect(fill = "black"),
        legend.text = element_text(colour = "grey50", size = 16),
        plot.title = element_text(face = "bold", colour = "grey50",
                                  hjust = 0.5, size = 16),
        panel.grid.major = element_line(colour = "grey10"),
        panel.grid.minor = element_line(colour = "grey10"),
        legend.position = "right",
        legend.margin = margin(0, 0, 0, 0),
        plot.margin = margin(5, 0, 5, 0),
        panel.border = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.text = element_text(colour = "grey50", size = 14),
        axis.title = element_text(colour = "grey50", size = 14))

ratio = 25.5/6.4
height = 3.5
width = height * ratio
ggsave(filename = "LinkedIn Banner.png", dpi = 300,
       width = width, height = height)


```

```{r, fig.width=8, fig.height=4.95, dpi=300, dev="png", message=FALSE, warning=FALSE}
electricity %>% 
  mutate(Zeitpunkt = round_date(Zeitpunkt, unit = "hour")) %>% 
  group_by(Zeitpunkt) %>% 
  summarise(kWh = sum(kWh, na.rm = T)) %>% 
  ungroup() %>%
  mutate(hour = hour(Zeitpunkt),
         week = week(Zeitpunkt)) %>% 
  group_by(hour, week) %>% 
  summarise(mean_c = median(kWh, na.rm = T)/1e6) %>% 
  ungroup() %>%
  ggplot(aes(y = hour + 1, x = week)) +
  geom_tile(aes(fill = mean_c), width=1, height=1, alpha = 0.9) +
  labs(title = NULL,
       y = NULL,
       x = NULL,
       fill = NULL) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(2, 52, 2)) +
  scale_y_reverse(expand = c(0, 0)) +
  guides(fill = "none") +
  scale_fill_gradient(low = "black", high = "azure",
                      labels = scales::comma_format(suffix = " GWh")) +
  theme(panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        legend.background = element_rect(fill = "black"),
        legend.key = element_rect(fill = "black"),
        legend.position = "bottom",
        legend.text = element_text(colour = "grey50", size = 12),
        legend.title = element_text(colour = "grey50"),
        legend.margin = margin(0, 0, 0, 0),
        plot.title = element_text(face = "bold", colour = "grey50",
                                  hjust = 0.5, size = 14),
        plot.subtitle = element_text(colour = "grey50", hjust = 0.5),
        panel.grid.major = element_line(colour = "grey10"),
        panel.grid.minor = element_line(colour = "grey10"),
        plot.margin = margin(10, 10, 10, 10),
        panel.border = element_blank(),
        axis.text = element_blank(),
        axis.title = element_text(colour = "grey50", size = 14))

ratio = 25.5/6.4
height = 3.5
width = height * ratio
ggsave(filename = "LinkedIn Banner2.png", dpi = 300,
       width = width, height = height)
```

Not only the mean, but also the confidence bands reveal a strong intra-year pattern, which in itself carries another weekly pattern shown in the heat map above. The lows during summer and Christmas holidays are considerable.

&nbsp;
<hr />
<p style="text-align: center;">A work by <a href="https://www.linkedin.com/in/mathias-steilen/">Mathias Steilen</a></p>
&nbsp;